### 2012-06-13 inst/examples/Sethi_policyfns.Rmd
updated plots of Sethi figure 3 includes net present value (value function) and escapement (policy function) for implementation, growth, and measurement uncertainty

``` {r plots}
require(reshape2)
policy <- melt( data.frame(stock=x_grid, implementation = x_grid[imp$D[,1]], measurement = x_grid[measure$D[,1]], growth = x_grid[growth$D[,1]]), id="stock")
value <-  melt(data.frame(stock=x_grid, implementation = imp$V, measurement = measure$V, growth = growth$V), id="stock")
ggplot(policy) + geom_point(aes(stock, stock-value, color=variable))
ggplot(value) + geom_point(aes(stock, stock-value, color=variable))
ggplot(policy) + geom_smooth(aes(stock, stock-value, color=variable))
ggplot(value) + geom_smooth(aes(stock, stock-value, color=variable))
````

>>>>

``` {r plots, fig.width=7}
require(reshape2)
policy <- melt( data.frame(stock=x_grid, implementation = x_grid[imp$D[,1]], measurement = x_grid[measure$D[,1]], growth = x_grid[growth$D[,1]]), id="stock")
value <-  melt(data.frame(stock=x_grid, implementation = imp$V, measurement = measure$V, growth = growth$V), id="stock")
ggplot(policy) + geom_point(aes(stock, stock-value, color=variable)) + ylab("escapement") 
ggplot(value) + geom_point(aes(stock, value, color=variable)) + ylab("Net Present Value")
ggplot(policy) + geom_smooth(aes(stock, stock-value, color=variable))+ ylab("escapement") 
ggplot(value) + geom_smooth(aes(stock, value, color=variable)) + ylab("Net Present Value")
````
